---
title: "IODS project-lectureday1"
author: "Rabbil Bhuiyan"
date: "31 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r child = "chapter1.Rmd"}
The course is intended to learn different tools for analyzing data, particularly by using rstudio. All the tasks completed using R will be linked and stored in Github account. The course also uses Datacamp for excercising the R tools to learn it.
https://github.com/bhuiyanluke/IODS-project/
  ```{r child = "chapter2.Rmd"}
- This week, from the begining of the lecture, I have learned using the Github and linked it to the rstudio. I had prior knowledge about rstudio but not in details. Linking the Github with rstudio was exciting. How to store the saved work in Github was very useful to me. The porcedure for storing the work in Github as follows:
-I opened the Github account
-Then fork it to the course repisotory as the instruction of the lecture
-Opened the Github desktop account
-And also cloned this with the course repisotory
-Opened the taks in rstudio and saved after editing
-Then commited to master in Github desktop
-Then I can see the changes in Github repisotory
Finally I stored all the work done in Gitbub and other people can also see my work
  
```
```{r child = "chapter3.Rmd"
```{r}
```

Reading data file into R 
url <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets"

# web address for math class data
url_math <- paste(url, "student-mat.csv", sep = "/")

# print out the address
url_math

# read the math class questionaire data into memory
math <- read.table(url_math, sep = ";" , header=TRUE)

# web address for portuguese class data
url_por <- paste(url, "student-por.csv", sep ="/")

# print out the address
url_por

# read the portuguese class questionaire data into memory
por <- read.table(url_por, sep = ";", header = TRUE)
# dimension of the data
dim(math)
dim(por)
# description of the variables: the both data set has 33 vairables.

# access the dplyr library
library(dplyr)


# common columns to use as identifiers
join_by <- c("school","sex","age","address","famsize","Pstatus","Medu","Fedu","Mjob","Fjob","reason","nursery","internet")

# join the two datasets by the selected identifiers
math_por <- inner_join(math, por, by = join_by, suffix = c(".math", ".por"))

# Strucure and dimension of the joined data set
str(math_por)
dim(math_por)

   

}


```
# description of cluster analysis



